---
title: "Credit Prediction Competition"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

```{r Loading in  packages}
library(dplyr)
library(fpp3)
library(ggplot2)
```

```{r reading in the data and turning it into a tsibble}
CREDIT <- read.csv("credit.csv")

Year <- as.data.frame(rep(5000:5040, each = 12))
Year <- sort(Year$`rep(5000:5040, each = 12)`, decreasing = TRUE) #reordering the dates so Credit is increasing
Month <- as.data.frame(rep(month.name, 41))
test <- data.frame(Year, Month)
names(test) <- c("Year","Month")
test$Year_Month <- paste(test$Year,test$Month)

CREDIT <- tsibble(Time = yearmonth(test$Year_Month),
             Credit = CREDIT$credit_in_millions,
             index = Time)

class(CREDIT) # make sure it's a tbl_ts
CREDIT %>% autoplot() # should be increasing

```

```{r checking the trends, differencing, transforming}
CREDIT %>% autoplot() #increasing trend check. Needs to be differenced.
CREDIT %>% gg_tsdisplay(Credit, plot_type = "partial") #suffers from autocorrealtion.
CREDIT %>% features(Credit, unitroot_kpss) #fails p-value test. Needs differencing.
CREDIT %>% features(Credit, unitroot_ndiffs) #needs one difference
CREDIT %>% features(Credit, unitroot_nsdiffs) #*Does not* need seasonal differencing.

# finding lambda
lambda <- CREDIT %>%
  features(Credit, features = guerrero) %>%
  pull(lambda_guerrero)

#Plot transformed series
CREDIT %>%
  autoplot(box_cox(Credit, lambda)) +
  labs(y = "",
       title = latex2exp::TeX(paste0(
         "Transformed Credit production with $\\lambda$ = ",
         round(lambda,2)))) 


#Plot differenced series
CREDIT %>% 
  gg_tsdisplay(difference(box_cox(Credit,lambda)),plot_type = "partial") #stationary at 0, ACF looks fine, first 4 lags appear correlated.

```
```


```{r}
credit_TR <- CREDIT %>% 
  stretch_tsibble(.init = 12, .step = 4)
  
#Simple Naive RMSE of 0.1587665
credit_TR %>% fill_gaps() %>% 
  model(naive = NAIVE(Credit)) %>% forecast(h = 12) %>% accuracy(CREDIT)

#Drift RMSE of 0.1579506
credit_TR %>% fill_gaps() %>% 
  model(drift = RW(box_cox(Credit,lambda))) %>% forecast(h = 12) %>% accuracy(CREDIT)

#models for trend
credit_TR %>% 
  fill_gaps() %>% 
  model(
    ETS = ETS(Credit ~ error("A") + trend("A") + season("N"))
  ) %>% 
  forecast( h = 12) %>% 
  accuracy(CREDIT)

#dampend holt's winters
credit_TR %>% 
  fill_gaps() %>% 
  model(
    DAMP_Holt = ETS(box_cox(Credit, lambda) ~ error("A") + trend("Ad", phi = .9) + season("N"))
  ) %>% 
  forecast( h = 12) %>% 
  accuracy(CREDIT) #damp holt RMSE of: 0.1457895

#Arima
credit_TR %>% 
  fill_gaps() %>% 
  model(
    ARIMA = ARIMA(box_cox(Credit, lambda))
  ) %>% 
  forecast(h = 12) %>% 
  accuracy(CREDIT) #RMSE of 0.134
  
#making at least one prediction using ARIMA since it is best model for me.
fit <- credit_TR %>% 
  fill_gaps() %>% 
  model(
    ARIMA = ARIMA(box_cox(Credit, lambda))
  ) 

fit %>% forecast(h=12) %>% 
  autoplot(CREDIT) +
  labs(y = "CREDIT", title = "Credits Earned Over Time")
#won't run. Receive an error of: provided data different key structure than forecast.
#I think this error is because I'm trying to autoplot credit, when forecast is credit_tr

```







